---
title: "Crime data preparation"
author: "Jun Chen"
date: "07/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

## Crime data preparation

```{r}
library(tidyverse)
library(dplyr)
```

input raw data and crime type mapping

```{r}
crime_data <- read.csv("[Data] Crime_Data_by_postcode.csv")
crime_type <- read.csv("[Mapping] Crime_Type.csv")
```


First, unselect columns (from column Jan.2010 to column Dec.2017) to extract dataset from 2018 to 2019.


Then gather the non-variable columns (from column Jan.2018 to column Dec.2019) into a two-column key-value pair (month_year, number_of_case).


Next, join with crime_type data with common variables (Offence.category, subcategory)


Finally, group data and summaries by Postcode and Crime.Type to show the total number of crime cases over 2018 to 2019.


```{r}
total_crime_18_19 <- crime_data %>%
  select(-(Jan.10:Dec.17)) %>%
  gather(month_year, number_of_case, Jan.18:Dec.19, na.rm = TRUE) %>%
  left_join(crime_type, c("Offence.category", "Subcategory")) %>%
  select(Postcode, Crime.Type, Offence.category, Subcategory, month_year, number_of_case) %>%
  group_by(Postcode, Crime.Type) %>%
  summarise(Total.Crime = sum(number_of_case)) %>%
  spread(Crime.Type, Total.Crime) %>%
  arrange(Postcode)
```