---
title: "School and Train data preparation"
author: "Jun Chen"
date: "07/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```


```{r, echo=FALSE}
library(geosphere)
library(tidyverse)
```

## School and train data preparation

First, input the raw data

```{r}
property_data <- read.csv("property_data_v3.csv")%>%
  select(id,longtitude,latitude)
station_data <- read.csv("./Distance From Train Station/[Data] NSW_Station_Entrances_Locations_2020.csv")
public_school_data <- read.csv("./Distance From Public School/[Data] NSW_public_schools_2016.csv")
private_school_data <- read.csv("./Distance From Non-Government School/[Data] NSW_non_government_school_2017.csv")
```


### Distance From the closest Public School

Using the longtitude and latitude data of properties and NSW public schools, calculate the distance between each property to each public school. Then choose the shortest distance for each property to form the "distance_from_closest_public_school" variable.

```{r}
temp <- round(distm(cbind(property_data$longtitude, property_data$latitude), cbind(public_school_data$Longitude, public_school_data$Latitude), fun = distGeo))/1000
for (i in 1:nrow(property_data)){
  public_school_number <- which(temp[i, ] == min(temp[i, ]))
  property_data$distance_from_closest_public_school[i] <- temp[i, public_school_number]
}
```


### Distance From the closest Non-Government School

Using the longtitude and latitude data of properties and NSW non-government schools, calculate the distance between each property to each non-government school. Then choose the shortest distance for each property to form the "distance_from_closest_private_school" variable.

```{r}
temp <- round(distm(cbind(property_data$longtitude, property_data$latitude), cbind(private_school_data$longtitude, private_school_data$latitude), fun = distGeo))/1000
for (i in 1:nrow(property_data)){
  private_school_number <- which(temp[i, ] == min(temp[i, ]))
  property_data$distance_from_closest_private_school[i] <- temp[i, private_school_number]
}
```

### Distance From Closest Entrance of Train Station


Using the longtitude and latitude data of properties and train station entrances, calculate the distance between each property to each train station entrance. Then choose the shortest distance for each property to form the "distance_from_closest_station" variable.

```{r}
temp <- round(distm(cbind(property_data$longtitude, property_data$latitude), cbind(station_data$LONG, station_data$LAT), fun = distGeo))/1000
for (i in 1:nrow(property_data)){
  station_entrance_number <- which(temp[i, ] == min(temp[i, ]))
  property_data$distance_from_closest_station[i] <- temp[i, station_entrance_number]
}
```